Investigating Interventions

### 2023-06-15 minos/validation/handovers.Rmd
adding nth order data to gee yj modules. tweaks to makefiles and notebooks so they run off relative paths.

---
title: "MINOS Handover Plots"
output:
  html_document:
    df_print: paged
---

@@

require(tidyverse)
require(ggplot2)
require(knitr)
require(here)

#workingDir <- "/home/luke/Documents/WORK/MINOS/"
workingDir <- normalizePath('../')
knitr::opts_knit$set(root.dir = workingDir)
rm(workingDir)
```

@@

```{r}
source(here::here('minos', 'utils_datain.R'))
source(here::here('minos', 'utils_validation_vis.R'))
```

@@

```{r}
# Read raw datafiles in
raw.files <- list.files(here::here('data', 'final_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
raw.dat <- do.call(rbind, lapply(raw.files, read.csv))

out.path <- here::here('output', 'default_config/')
base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
```

@@

```{r}
start.year <- 2020
save.path <- here::here("plots", "handovers")
#create.if.not.exists(save.path)
```

@@

## Financial Situation

```{r}
raw.financial_situation <- raw.dat %>% 
  dplyr::select(pidp, time, financial_situation) %>%
  group_by(time, financial_situation) %>%
  count() %>%
  mutate(source = 'final_US')

base.financial_situation <- base.dat %>%
  dplyr::select(pidp, time, financial_situation) %>%
  group_by(time, financial_situation) %>%
  count() %>%
  mutate(source = 'baseline_output')

# merge before plot
financial_situation <- rbind(raw.financial_situation, base.financial_situation)
financial_situation$financial_situation <- as.factor(financial_situation$financial_situation)

# Now plot
ggplot(data = financial_situation, mapping = aes(x = time, y = n, group = financial_situation, colour = financial_situation)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Financial Situation', subtitle = 'Counts by Level') +
  xlab('Year') +
  ylab('Count')

financial_situation.norm <- financial_situation %>%
  group_by(time) %>%
  mutate(total = sum(n)) %>%
  mutate(prct = (n / total))

ggplot(data = financial_situation.norm, mapping = aes(x = time, y = prct, fill=financial_situation)) +
  geom_bar(stat = 'identity') +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Financial situation') +
  xlab('Year') +
  ylab('Proportion')

ggsave(filename = 'financial_situation.png',
       plot = last_plot(),
       path = save.path)

>>>>

---
title: "MINOS Handover Plots"
output: html_notebook
---

@@

require(tidyverse)
require(ggplot2)

#workingDir <- "/home/luke/Documents/WORK/MINOS/"
workingDir <- "/Users/robertclay/"
knitr::opts_knit$set(root.dir = workingDir)
rm(workingDir)
```

@@

```{r}
source('/Users/robertclay/minos/minos/utils_datain.R')
source('/Users/robertclay/minos/minos/utils_validation_vis.R')
```

@@

```{r}
# Read raw datafiles in
raw.files <- list.files('/Users/robertclay/minos/data/final_US/', pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
raw.dat <- do.call(rbind, lapply(raw.files, read.csv))

out.path <- '/Users/robertclay/minos/output/default_config/'
base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
```

@@

```{r}
start.year <- 2020

save.path <- '/Users/robertclay/minos/plots/andovers/'
```

@@

### 2023-06-15 minos/validation/interventions.Rmd
adding nth order data to gee yj modules. tweaks to makefiles and notebooks so they run off relative paths.

```{r}
income.base <- base %>% 
  select(pidp, time, hh_income)
income.energy <- energy %>% 
  select(pidp, time, hh_income, income_boosted)
# first rename and cbind
income.b <- rename(income.base, base = hh_income)
income.e <- rename(income.energy, energy = hh_income)
income.merged <- merge(income.b, income.e, by=c('pidp', 'time'))
income.merged <- pivot_longer(data = income.merged,
                              cols = base:energy,
                              names_to = 'scenario',
                              values_to = 'hh_income')
income.merged.byyr <- income.merged %>%
  group_by(time, scenario) %>%
  summarise(hh_income = mean(hh_income))
ggplot(data = income.merged.byyr, mapping = aes(x = time, y = hh_income, color=scenario)) +
  geom_line()
```

## SF_12

```{r}
sf12.base <- base %>% 
  select(pidp, time, SF_12)
sf12.energy <- energy %>% 
  select(pidp, time, SF_12, income_boosted)
# first rename and cbind
sf12.b <- rename(sf12.base, base = SF_12)
sf12.e <- rename(sf12.energy, energy = SF_12)
sf12.merged <- merge(sf12.b, sf12.e, by=c('pidp', 'time'))
sf12.merged <- pivot_longer(data = sf12.merged,
                              cols = base:energy,
                              names_to = 'scenario',
                              values_to = 'SF_12')
sf12.merged.byyr <- sf12.merged %>%
  group_by(time, scenario) %>%
  summarise(SF_12 = mean(SF_12))
ggplot(data = sf12.merged.byyr, mapping = aes(x = time, y = SF_12, color=scenario)) +
  geom_line()
```

## Boost Amount
```{r}
income.energy <- energy %>% 
  select(pidp, time, hh_income, income_boosted, boost_amount)
income.energy.byyr <- income.energy %>%
  group_by(time) %>%
  summarise(boost_amount = mean(boost_amount))
ggplot(data = income.energy.byyr, mapping = aes(x = time, y = boost_amount)) +
  geom_line()
```

@@

```{r}
income.base <- base %>% 
  select(pidp, time, hh_income)
income.child <- allchild %>% 
  select(pidp, time, hh_income, income_boosted)
# first rename and cbind
income.base <- rename(income.base, base = hh_income)
income.child <- rename(income.child, allchild = hh_income)
income.merged <- merge(income.base, income.child, by=c('pidp', 'time'))
income.merged <- pivot_longer(data = income.merged,
                              cols = base:allchild,
                              names_to = 'scenario',
                              values_to = 'hh_income')
income.merged.byyr <- income.merged %>%
  group_by(time, scenario) %>%
  summarise(hh_income = mean(hh_income))
ggplot(data = income.merged.byyr, mapping = aes(x = time, y = hh_income, color=scenario)) +
  geom_line()
```
```{r}
income.child <- allchild %>% 
  select(pidp, time, hh_income, income_boosted, boost_amount)
income.child.byyr <- income.child %>%
  group_by(time) %>%
  summarise(boost_amount = mean(boost_amount))
ggplot(data = income.child.byyr, mapping = aes(x = time, y = boost_amount)) +
  geom_line()
```

```{r}
boosted.byyr <- income.child %>% 
  group_by(time) %>%
  count(income_boosted)
ggplot(data = filter(boosted.byyr, income_boosted == 'True'), mapping = aes(x = time, y = n)) +
  geom_line()
ggplot(data = boosted.byyr, mapping = aes(x = time, y = n, color = income_boosted)) +
  geom_line()
```

>>>>

```{r}
income.base <- base %>% 
  select(pidp, time, hh_income)
income.energy <- energy %>% 
  select(pidp, time, hh_income, income_boosted)
# first rename and cbind
income.b <- rename(income.base, base = hh_income)
income.e <- rename(income.energy, energy = hh_income)
income.merged <- merge(income.b, income.e, by=c('pidp', 'time'))
income.merged <- pivot_longer(data = income.merged,
                              cols = base:energy,
                              names_to = 'scenario',
                              values_to = 'hh_income')
income.merged.byyr <- income.merged %>%
  group_by(time, scenario) %>%
  summarise(hh_income = mean(hh_income))
ggplot(data = income.merged.byyr, mapping = aes(x = time, y = hh_income, color=scenario)) +
  geom_line()
```
## SF_12
```{r}
sf12.base <- base %>% 
  select(pidp, time, SF_12)
sf12.energy <- energy %>% 
  select(pidp, time, SF_12, income_boosted)
# first rename and cbind
sf12.b <- rename(sf12.base, base = SF_12)
sf12.e <- rename(sf12.energy, energy = SF_12)
sf12.merged <- merge(sf12.b, sf12.e, by=c('pidp', 'time'))
sf12.merged <- pivot_longer(data = sf12.merged,
                              cols = base:energy,
                              names_to = 'scenario',
                              values_to = 'SF_12')
sf12.merged.byyr <- sf12.merged %>%
  group_by(time, scenario) %>%
  summarise(SF_12 = mean(SF_12))
ggplot(data = sf12.merged.byyr, mapping = aes(x = time, y = SF_12, color=scenario)) +
  geom_line()
```

## Boost Amount
```{r}
income.energy <- energy %>% 
  select(pidp, time, hh_income, income_boosted, boost_amount)
income.energy.byyr <- income.energy %>%
  group_by(time) %>%
  summarise(boost_amount = mean(boost_amount))
ggplot(data = income.energy.byyr, mapping = aes(x = time, y = boost_amount)) +
  geom_line()
```
## Who Boosted?

@@

```{r}
income.base <- base %>% 
  select(pidp, time, hh_income)
income.child <- allchild %>% 
  select(pidp, time, hh_income, income_boosted)
# first rename and cbind
income.base <- rename(income.base, base = hh_income)
income.child <- rename(income.child, allchild = hh_income)
income.merged <- merge(income.base, income.child, by=c('pidp', 'time'))
income.merged <- pivot_longer(data = income.merged,
                              cols = base:allchild,
                              names_to = 'scenario',
                              values_to = 'hh_income')
income.merged.byyr <- income.merged %>%
  group_by(time, scenario) %>%
  summarise(hh_income = mean(hh_income))
ggplot(data = income.merged.byyr, mapping = aes(x = time, y = hh_income, color=scenario)) +
  geom_line()
```
```{r}
income.child <- allchild %>% 
  select(pidp, time, hh_income, income_boosted, boost_amount)
income.child.byyr <- income.child %>%
  group_by(time) %>%
  summarise(boost_amount = mean(boost_amount))
ggplot(data = income.child.byyr, mapping = aes(x = time, y = boost_amount)) +
  geom_line()
```
## Who Boosted?
```{r}
boosted.byyr <- income.child %>% 
  group_by(time) %>%
  count(income_boosted)
ggplot(data = filter(boosted.byyr, income_boosted == 'True'), mapping = aes(x = time, y = n)) +
  geom_line()
ggplot(data = boosted.byyr, mapping = aes(x = time, y = n, color = income_boosted)) +
  geom_line()
```
